Anomalous waves triggered by abrupt depth changes: experiments and truncated KdV theory

### 2019-10-10 paper2_JNLS/paper.tex
NM

	We thus run the with these model parameters (and with a sufficiently fine timestep, and number of samples, and to a final dimensionless time of 10).

	\vsp{5}

>>>>

	In Fig.~\ref{uhist} we show the displacement distributions that were measured in the experiments (top row) versus those that emerge from a mixed long-time/ensemble average of the TKdV simulations (bottom row). 	
	\vsp{5}
